Appendix: A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-04 appendix.Rmd
modify the alpha table

```{r sensitivity, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line indicates $p\\text{-value} = 0.05$. The area coloured in red indicates $\\text{adjusted }p\\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multipliers smaller than 1, the adjusted $p\\text{-value}$ will initially increase and decline when the $p\\text{-value}$ increases. The trend is opposite with multipliers greater than $1$, but the difference eventually reaches $0$."}

@@

```{r}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  group_by(modified) %>%
  count(adjusted_reject = adjusted_p_value <= 0.05, reject = p_value <= 0.05) %>%
  complete(adjusted_reject, reject, fill = list(n = 0)) %>%
  ungroup() %>%
  filter(adjusted_reject != reject) %>%
  mutate(case = ifelse(!adjusted_reject, "reject to not reject", "not reject to reject")) %>%
  rename(fraction = modified) %>%
  mutate(n = paste0(round(n/279 * 100, 2))) %>%
  select(-adjusted_reject, -reject) %>%
  pivot_wider(names_from = case, values_from = n) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "sensitivity", 
                    escape = FALSE,
                    caption = "Examining how decisions might change if $\\hat{\\alpha}$ was different. Percentage of lineups that where the $p$-value would switch to above or below 0.05, when $\\hat{\\alpha}$ is varied by a fractional amount.")
```

@@

map_df(seq(1, 11, 2), ~eval_n(.x, 1)) %>%
  select(-boot_id) %>%
  nest(c(effect_size, reject, offset0)) %>%
  mutate(mod = map(data, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-data, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = factor(n_eval)),
            size = 1) +
  labs(col = "N. evals") +
  xlab(expression(log[e] (Effect_size))) +
  theme_light() +
  scale_color_brewer(palette = "Reds")
```

>>>>

```{r sensitivity, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. Only lineups with uniform fitted value distribution is used. The vertical dashed line indicates $p\\text{-value} = 0.05$. The area coloured in red indicates $\\text{adjusted }p\\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multipliers smaller than 1, the adjusted $p\\text{-value}$ will initially increase and decline when the $p\\text{-value}$ increases. The trend is opposite with multipliers greater than $1$, but the difference eventually reaches $0$."}

@@

```{r}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  group_by(modified) %>%
  count(adjusted_reject = adjusted_p_value <= 0.05, reject = p_value <= 0.05) %>%
  complete(adjusted_reject, reject, fill = list(n = 0)) %>%
  ungroup() %>%
  filter(adjusted_reject != reject) %>%
  mutate(case = ifelse(!adjusted_reject, "reject to not reject", "not reject to reject")) %>%
  rename(multiplier = modified) %>%
  select(-adjusted_reject, -reject) %>%
  pivot_wider(names_from = case, values_from = n) %>%
  mutate(reject_not_reject_per = round(`reject to not reject`/279*100, 2)) %>%
  mutate(not_reject_reject_per = round(`not reject to reject`/279*100, 2)) %>%
  select(multiplier,
         `reject to not reject`,
         reject_not_reject_per,
         `not reject to reject`,
         not_reject_reject_per) %>%
  kableExtra::kable(format = "latex", 
                    booktabs = TRUE,
                    col.names = c("Multiplier",
                                  "Reject to not reject",
                                  "%",
                                  "Not reject to reject",
                                  "%"),
                    label = "sensitivity", 
                    caption = "Examining how decisions might change if $\\hat{\\alpha}$ was different. Percentage of lineups that where the $p$-value would switch to above or below 0.05, when $\\hat{\\alpha}$ is multiplied by a multiplier.") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

@@

map_df(seq(1, 11, 2), ~eval_n(.x, 1)) %>%
  select(-boot_id) %>%
  nest(c(effect_size, reject, offset0)) %>%
  mutate(mod = map(data, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-data, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = factor(n_eval)),
            size = 1) +
  labs(col = "#Evaluations") +
  ylab("Power") +
  xlab(expression(log[e] (Effect_size))) +
  theme_light() +
  scale_color_brewer(palette = "Reds")
```

### 2023-04-04 appendix.tex
modify the alpha table

\caption{Change of $p$-values with $\hat{\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line indicates $p\text{-value} = 0.05$. The area coloured in red indicates $\text{adjusted }p\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multipliers smaller than 1, the adjusted $p\text{-value}$ will initially increase and decline when the $p\text{-value}$ increases. The trend is opposite with multipliers greater than $1$, but the difference eventually reaches $0$.}\label{fig:sensitivity}
\end{figure}

@@

\caption{\label{tab:sensitivity}Examining how decisions might change if $\hat{\alpha}$ was different. Percentage of lineups that where the $p$-value would switch to above or below 0.05, when $\hat{\alpha}$ is varied by a fractional amount.}
\centering
\begin{tabular}[t]{rll}
\toprule
fraction & reject to not reject & not reject to reject\\
\midrule
0.500 & 2.51 & 0\\
0.750 & 1.43 & 0\\
0.875 & 1.08 & 0\\
1.125 & 0 & 1.08\\
1.250 & 0 & 1.43\\
\addlinespace
1.500 & 0 & 1.79\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{Change of $p$-values with $\hat{\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. Only lineups with uniform fitted value distribution is used. The vertical dashed line indicates $p\text{-value} = 0.05$. The area coloured in red indicates $\text{adjusted }p\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multipliers smaller than 1, the adjusted $p\text{-value}$ will initially increase and decline when the $p\text{-value}$ increases. The trend is opposite with multipliers greater than $1$, but the difference eventually reaches $0$.}\label{fig:sensitivity}
\end{figure}

@@

\caption{\label{tab:sensitivity}Examining how decisions might change if $\hat{\alpha}$ was different. Percentage of lineups that where the $p$-value would switch to above or below 0.05, when $\hat{\alpha}$ is multiplied by a multiplier.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rrrrr}
\toprule
Multiplier & Reject to not reject & \% & Not reject to reject & \%\\
\midrule
0.500 & 7 & 2.51 & 0 & 0.00\\
0.750 & 4 & 1.43 & 0 & 0.00\\
0.875 & 3 & 1.08 & 0 & 0.00\\
1.125 & 0 & 0.00 & 3 & 1.08\\
1.250 & 0 & 0.00 & 4 & 1.43\\
\addlinespace
1.500 & 0 & 0.00 & 5 & 1.79\\
\bottomrule
\end{tabular}}
\end{table}
